% $Id$

This section summarizes the project milestones and the expected outcomes.

\subsection{\label{ssec:plan}Milestones}

Based on Section~\ref{ssec:aims}, we break down time scale needed to develop
each component as belows. The milestones would like more ``conceptual'' rather
than practical or tangible. The project dates listed below are only indicative
as the project will evolve based on the results being obtained while working on
it.

\paragraph{\textsf{May 26}} \underline{\textbf{GSoC Project Start}}

\paragraph{\textsf{May 31}} Finish background research and readings: \emph{vic} source
codes and UltraGrid's TFRC implementation along with RTP extension part.  The
aim here is try looking at how TFRC was implemented over a \emph{vic}-like platform
(different library and different language so it would not be possible to
directly re-use them.).

\paragraph{\textsf{Jun. 6}} Commit necessary TFRC files - e.g., TFRC
(\texttt{tfrc\_sndr.cpp, tfrc\_rcvr.cpp}, etc), RTP integration
(\texttt{rtp\_tfrc.cpp}, etc), CC handler (\texttt{cc.cpp}, etc). It would not
be necessariliy a full implementation at this stage yet.

\paragraph{\textsf{Jun. 20}} Primitive TFRC implementation. At this stage, we
should be able to send a packet using TFRC (with dummy packets).

\paragraph{\textsf{Jun. 27}} Commit necessary TFWC files. It would not be
necessariliy a full implementation at this stage yet.

\paragraph{\textsf{Juil. 4}} Primitive TFWC implementation

\paragraph{\textsf{Jul. 7}} \underline{\textbf{Mid-term Evaluation}} -- Write
interim report: what has been obtained successfully and what has not, what
should be changed for the final project goal, etc.

\paragraph{\textsf{Jul. 18}} Examine what feedback information can be used to
codecs.  (e.g., modify codecs? or use Q-factor in a specific codec?, etc)

\paragraph{\textsf{Jul. 25}} Finalizing TFR(W)C interactioin with codecs.

\paragraph{\textsf{Aug. 1}} Test and Evaluation for the whole systems.

\paragraph{\textsf{Aug. 8}} Final evaluation and discussion

\paragraph{\textsf{Aug. 15}} Come up with final version of source codes and a
report.

\paragraph{\textsf{Aug. 18}} \underline{\textbf{Project Submission}}-- Submit
the results to Google and wrap-up.


\subsection{\label{ssec:codes}Program Source Code}

\begin{itemize} 
\item Congestion Control Modules (TFRC and TFWC) 
\item RTP Interface with CC Modules 
\item Video codec Enhancement 
\end{itemize}

\subsection{\label{ssec:docs}Reports}


\begin{itemize}
\item Interim Report
\item Final Report with Results
\end{itemize}

\newpage
